Postural changes mediate children's visual access to social information

### 2018-01-13 writeup-cogsci-copy/cogsci2018.Rmd
merged detection figures, wrote more results text

```{r posture fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion time that infants in each age group spent in each posture (left panel) and orientation relative to their caregiver (right  panel)." }

@@

# Changes in Access to Faces

Next, we examined the impact of these changes

```{r fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion face (left) and hand (right) detections as a function of participant's age. Note that the axes are different; hands were detected overall much less frequently in this dataset." }
detectionsByAge <- dlong %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(detections = mean(detection)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

@@

```{r faceByPostureFig, fig.env="figure*", fig.pos = "h", fig.align = "center", num.cols.cap=2, fig.width=7, fig.height=3, fig.cap = "Proportion of face detections as a function of infant's orientation, using the MTCNN3 face detections and OpenPose face detections (left two panels) and the proportion of hand detections as a function of infant's orientation, using OpenPose hand detections and the OpenPose wrist detections."}

@@

ggplot(detectionsByPosture, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw()

@@

```{r faceByOrientFig, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, num.cols.cap=2, fig.cap = "sing the MTCNN3 face detections and OpenPose face detections (left two panels) and the proportion of hand detections as a function of infant's posture, using OpenPose hand detections and the OpenPose wrist detections" }
detectionsByPosture <- dlong %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid,detectorType) %>%
  summarise(detections = mean(detection)) %>%
  group_by(age.grp)

ggplot(detectionsByPosture, aes(x = factor(age.grp), y = detections, col = orientation)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw() 
```

@@

```{r echo=FALSE, include=FALSE}
d$faceNum=as.numeric(d$faceMT)
d$handNum=as.numeric(d$handOP)

# Fails to converge
# fullModel <- glmer(is_face ~ scale(age.at.test)*(posture) *(orientation) + (1|subid),
#       data = d,
#       family = "binomial")

# Fails to converge
# agexOrientation <- glmer(faceNum ~ scale(age.at.test) * orientation + (1|subid),
#       data = d,
#       family = "binomial")

fullModelminsInt_Faces <- glmer(faceNum ~ scale(age.at.test) + posture + orientation + (1|subid),
       data = d,
       family = "binomial")

fullModelminsInt_Handd <- glmer(handNum ~ scale(age.at.test) + posture + orientation + (1|subid),
       data = d,
       family = "binomial")

ageOnly <- glmer(faceNum ~ scale(age.at.test) + (1|subid),
      data = d,
      family = "binomial")

@@

```{r xtable, results="asis"}
tab2 <- xtable::xtable(summary(fullModelminsInt_Faces)$coef, digits=3,
                      caption = "Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across                       the entire dataset.")

print(tab2, type="latex", comment = F, table.placement = "H")
```

```{r xtable, results="asis"}
tab2 <- xtable::xtable(summary(fullModelminsInt_Hands)$coef, digits=3,
                      caption = "Results from GLMM model prediting the presence/absence of a hands (OpenPose-Hands) across                       the entire dataset.")

print(tab2, type="latex", comment = F, table.placement = "H")
```

@@

>>>>

```{r posture, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion time that infants in each age group spent in each posture (left panel) and orientation relative to their caregiver (right  panel)." }

@@

# Changes in Access to Faces & Hands

 We first examined the proportion of face and hand detections across age; a full summary can be seen in Figure \ref{fig:detsbyAge}. We observed  a slight u-shaped function both when analyzing the output of the MTCNN and OpenPose detectors, such that 12-month-olds may experience less faces than 8 or 12-month-olds. Next, we observed that hand detections increased with the age of the participant, though they were relatively infrequent in this dataset. As expected, we found that wrist detections we relatively more frequent and also appeared to increase somewhat with age, suggesting that caregivers hands may be just outside of the field of view of our camera or that they were often occluded by toys.

Next, we turned to our hypothesis of interest, examinig the impact of postural and locomotive developments on children's visual access to faces and hands. Overall, we ofund that children's posture was a major factor both in how many faces they saw during the play session. Infants who were sitting saw mor faces than infants who were lying down or being carried, while infants who were standing saw the most faces.

```{r detByAge, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion face (left) and hand (right) detections as a function of participant's age. Note that the axes are different; hands were detected overall much less frequently in this dataset." }
detectionsByAge <- dlong %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test, detectorType) %>%
  summarise(detections = mean(detection)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len.min))

@@

```{r faceByPostureFig, fig.env="figure*", fig.pos = "h", fig.align = "center", num.cols.cap=2, fig.width=7, fig.height=6, fig.cap = "Proportion of face/hand detections as a function of infant's posture (top panels) and orientation (bottom panels), using the MTCNN3 face detections and OpenPose face detections (left two panels) and using OpenPose hand detections and the OpenPose wrist detections (right two panels)."}

@@

p1=ggplot(detectionsByPosture, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw()

detectionsByOrientation <- dlong %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid,detectorType) %>%
  summarise(detections = mean(detection)) %>%
  group_by(age.grp)

p2=ggplot(detectionsByOrientation, aes(x = factor(age.grp), y = detections, col = orientation)) + 
  geom_boxplot() + 
  ylab("Proportion  Detections") + 
  xlab("Age (months)") + 
  facet_grid(~detectorType) +
  theme_bw()

grid.arrange(p1,p2, nrow=2)

@@

```{r faceByOrientFig, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, num.cols.cap=2, fig.cap = "sing the MTCNN3 face detections and OpenPose face detections (left two panels) and the proportion of hand detections as a function of infant's posture, using OpenPose hand detections and the OpenPose wrist detections" }

@@

<!-- ```{r echo=FALSE, include=FALSE} -->
<!-- d$faceNum=as.numeric(d$faceMT) -->
<!-- d$handNum=as.numeric(d$handOP) -->

<!-- # Fails to converge -->
<!-- # fullModel <- glmer(is_face ~ scale(age.at.test)*(posture) *(orientation) + (1|subid), -->
<!-- #       data = d, -->
<!-- #       family = "binomial") -->

<!-- # Fails to converge -->
<!-- # agexOrientation <- glmer(faceNum ~ scale(age.at.test) * orientation + (1|subid), -->
<!-- #       data = d, -->
<!-- #       family = "binomial") -->

<!-- fullModelminsInt_Faces <- glmer(faceNum ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->

<!-- fullModelminsInt_Handd <- glmer(handNum ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->

<!-- ageOnly <- glmer(faceNum ~ scale(age.at.test) + (1|subid), -->
<!--       data = d, -->
<!--       family = "binomial") -->

<!-- ``` -->

@@

<!-- ```{r xtable, results="asis"} -->
<!-- tab2 <- xtable::xtable(summary(fullModelminsInt_Faces)$coef, digits=3, -->
<!--                       caption = "Results from GLMM model prediting the presence/absence of a face (MTCNN-Faces) across the entire dataset.") -->

<!-- print(tab2, type="latex", comment = F, table.placement = "H") -->
<!-- ``` -->

<!-- ```{r xtable, results="asis"} -->
<!-- tab3 <- xtable::xtable(summary(fullModelminsInt_Handd)$coef, digits=3, -->
<!--                       caption = "Results from GLMM model prediting the presence/absence of a hands (OpenPose-Hands) across the entire dataset.") -->

<!-- print(tab3, type="latex", comment = F, table.placement = "H") -->
<!-- ``` -->

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -8.775 & 0.236 & -37.259 & 0.000 \\ 
  Age & 0.879 & 0.166 & 5.292 & 0.000 \\ 
  Posture-Prone  & 1.215 & 0.110 & 11.082 & 0.000 \\ 
  Posture-Sit & 1.943 & 0.108 & 18.000 & 0.000 \\ 
  Posture-Stand  & 2.175 & 0.107 & 20.260 & 0.000 \\ 
  Orient.-Close  & 0.608 & 0.059 & 10.371 & 0.000 \\ 
  Orient.-Far & 2.244 & 0.060 & 37.222 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of hands (OpenPose-Hands) across the entire dataset.} 
\end{table}
